---
title: "Drop Procedure"
format: html
---

# Article selection procedure

```{r}
library(dplyr)
library(PRISMAstatement)
```

```{r}
df_papers <- read.csv("data/Papers imported_exported_1.csv")
count(df_papers, source)
n_dupes_merged <- nrow(filter(df_papers, source == "pubmed, wos"))
n_dupes_found <- nrow(filter(df_papers, SelectionPhase1 == "Duplicate"))
n_dupes_total <- n_dupes_merged + n_dupes_found

n_screened <- nrow(df_papers)
n_found <- n_screened + n_dupes_merged

n_phase1_kept <- nrow(filter(df_papers, SelectionPhase1 == "Good"))
n_phase1_dropped <- n_screened - n_phase1_kept

n_phase2_kept <- nrow(filter(df_papers, FinalSelected == "YES"))
n_phase2_kept_notreviews <- nrow(filter(df_papers, FinalSelected == "YES" & !IsReview))


n_phase2_tied <- nrow(filter(df_papers, FinalAnswered == 4, FinalGoodSum == 2))
n_phase2_tied_kept <- nrow(filter(df_papers, FinalAnswered == 4, FinalGoodSum == 2, FinalSelected == "YES"))

n_phase2_dropped <- n_phase1_kept - n_phase2_kept

n_phase3_kept_all <- nrow(filter(df_papers,
                        FinalSelected == "YES", 
                        Phase3DropReason == ""))

n_phase3_kept_reviews <- nrow(filter(df_papers, 
                                FinalSelected == "YES", 
                                Phase3DropReason == "",
                                IsReview == TRUE))
n_phase3_kept_notreviews <- n_phase3_kept_all - n_phase3_kept_reviews

n_phase3_dropped_all <- n_phase2_kept - n_phase3_kept_all
n_phase3_dropped_not_reviews <- n_phase3_dropped_all - n_phase3_kept_reviews
```

A total of `r n_found` papers were identified using the search query on WOS and pubmed. These were merged and `r n_dupes_merged` duplicates were found during this automated process. This left a `r n_screened` papers to be screened. 

These were prescanned by 5 researchers, each receiving a portion of the dataset and considering the inclusion of the paper based on its title, keywords and abstract. In this phase, we included even papers with weak links to the topic, to be later fully considered in the second full text search. Papers were discarded based on various criteria, mainly if they were not focusing on mental health, but rather physical therapy, not offering digital therapy, not being multi user, targetting very limited ungeneralizable populations, being protocols of studies, not conducted studies etc. This preliminary search left us with `r n_phase1_kept` papers.

These papers were each considered by five researchers, each receiving them in a random order. The researchers studied the fulltext of the paper and categorized it similarly to previous criteria (e.g. not offering multi user experience, focusing on limited populations). If a paper received three positive votes for inclusion, it was kept in the final review, if it received 3 negative points, it was excluded. Articles with two points for and two against were again addressed as a group (this included `r n_phase2_tied` papers) and another `r n_phase2_tied_kept` papers were added.

The final sample included `r n_phase3_kept_notreviews` papers and `r n_phase3_kept_reviews` reviews. The reviews were not included in the qualitative synthesis.

## Prisma chart

```{r}
prisma(found = n_found,
       found_other = 0,
       no_dupes = n_screened,
       screened = n_screened,
       screen_exclusions = n_phase1_dropped,
       full_text = n_phase1_kept,
       full_text_exclusions = n_phase2_dropped,
       qualitative = n_phase3_kept_notreviews)
```
